% Chapter 8

\begin{savequote}[\quotewidth]
``Begin at the beginning," the King said, very gravely, ``and go on till you come to the end: then stop''.
\qauthor{Lewis Carroll}
\end{savequote}

\chapter{Conclusion} % Main chapter title

\zlabel{chap:pdfstartpage} % For hyperref: this makes this the default page to open when the PDF opens.
\todo{Move zlabel{chap:pdfstartpage} to appropriate chapter. Remove before publication}
\todo{Remove usepackage{stampinclude} before publication.}

\label{Chapter8} % For referencing this chapter elsewhere, use \ref{Chapter8}


%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Introduction}

The world needs to change. If not you, who? If not now, when?

\section{Synopsis}

\subsection{Chapter \ref{Chapter1}: \nameref{Chapter1} }

The molecular basis of sustainability \autocite{Anastas2016} demands that
chemists discuss sustainability in terms of compounds. Chapter \ref{Chapter1}
opens with the idea that energy is an essential component of industrialized
societies, but that choosing of fossil fuels as our source of energy causes
pollution, which threatens to nullify the benefits they bring. It describes the
process which causes carbon dioxide to be emitted in large quantities, and how its
interaction with planetary radiation makes it a pollutant. The concept of
``carbon footprint'' is introduced, which allows the comparison of activities in
terms of their carbon pollution, enabling allows decision makers to select the
least polluting option. The discussion then focuses on internal-combustion
engines, which is a major source of carbon and noxious pollution, and it is
shown that higher-efficiency engines have lower carbon footprints. A discussion
of ways to reduce the carbon footprint of internal combustion engines shows
that, in the cases where they cannot be replaced by electric motors, a reduction
of carbon footprint can be obtained by preferring large, high-performance Diesel
engines fuelled by biodiesel. The discussion concludes with the idea that the
success of such engines will demand high quality biodiesel, and that
chromatography will play a central role in ensuring that quality.

\subsection{Chapter \ref{Chapter2}: \nameref{Chapter2} }

Chapter \ref{Chapter2} starts with a discussion of the chemical industry and the
need to move towards ``green'' chemistry. It introduces carbon dioxide as a
renewable resource, discusses its various uses in industry, and then focuses on
its application in extraction and chromatography. It describes how carbon
dioxide becomes a solvent at high pressures and densities, and then introduces
supercritical fluid chromatography (SFC). Fractions of eluate from SFC can be
analysed by gas chromatography, and if a suitable set of criteria is met, then
the combination is called SFC×GC.

\subsection{Chapter \ref{Chapter3}: \nameref{Chapter3} }

As discussed in Chapter \ref{Chapter1}, a reliable high-performance engine
requires a reliable fuel. Chapter \ref{Chapter3} discusses the concepts of
technical standards, which establishes requirements with which fuels must
comply. The discussion then focuses on the technical standard SANS 1935, which
lists the requirements that biodiesel offered for sale in South Africa must
comply with, concluding with the role chromatography plays in 

\subsection{Chapter \ref{Chapter4}: \nameref{Chapter4} }

Chapter \ref{Chapter4} explains the experimental equipment used for
chromatography using high-pressure carbon dioxide as a mobile phase. It starts
with describing the mobile phase, how it is stored and pumped, how modifier is
added, and how the sample is injected. It describes problems with designing the
restrictor that maintains the pressure, and concludes with remarks about using a
gas chromatograph as a detector for SFC. 

\subsection{Chapter \ref{Chapter5}: \nameref{Chapter5} }

Chapter \ref{Chapter5} opens with a discussion on the time aspect of
comprehensive SFC×GC chromatography, and shows that for practical analysis the
GC dimension must be \textit{fast}. The theory of fast GC is discussed, which
leads to the the need for fast temperature programming. The design of a
resistively heated coaxial heater is described, including its calibration and
control. The discussion then covers the need for a cold column, and the design
of coaxial cooling using boiling liquid carbon dioxide is described. Next, the
discussion covers the design of hardware to mount the coaxial heater of the fast
GC in a conventional GC oven. The chapter concludes with a description of the
detector and the data flow from signal to final chromatogram.

\subsection{Chapter \ref{Chapter6}: \nameref{Chapter6} }

Chapter \ref{Chapter6} discusses the application of the developed SFC×GC
instrument to the study of fatty acid profiles of various potential biodiesel
feedstocks, and shows that SFC×GC can be used to separate biodiesel from
petrodiesel in biodiesel blends.

\subsection{Chapter \ref{Chapter7}: \nameref{Chapter7} }

Chapter \ref{Chapter7} demonstrates that the use of SFC with modifiers does not
preclude the use of the flame ionization detector when GC is used as a second
dimension.

\section{Contributions of this study}

The research presented in this thesis contributes to the field of chromatography in the following aspects:

\subsection{Coaxial heater cooling}

The biggest new contribution is proving the concept of active cooling of short
chromatography columns using precisely-applied carbon dioxide. To the best of
our knowledge there is no other fast temperature-programmed chromatograph that
that has sub-ambient ramp start temperatures or a faster repetition rate. 

\subsection{Coaxial heater reliability}

The success of the SFC×GC is undoubtedly attributable to the high repeatability of the fast temperature programming. The 

\subsection{Length of SFC column}


\section{Voids in this study} 

\subsection{Lack of optimization}

\subsection{Luck with voltage ranges}

\section{Design}

Although this was a scientific project, I learned a lot about design. If I'd start the project again 

\section{Disasters}

\subsection{About the isolation amplifier}

\subsection{Thinking that we'd elute alcohols}

We could separate paraffins, olefins and aromatics, using the long column.

\subsection{Variable modulation period}

It is possible to vary the modulation period during an SFC×GC run. This would
allow one to speed up analysis, by collecting fewer fractions where less
information would be expected.

\section{Limitations of this SFC×GC design}

\subsection{Cooling control}
The fast GC temperature was poorly controlled in the \SIrange{-20}{50}{\celsius}
region of the temperature ramps, because the coaxial heater was not isolated. It
was mounted in a GC oven, together with the heated T-piece blocks. The heat
leaking from these uninsulated blocks accumulated in the oven, until the oven
reached a temperature of about \SI{50}{\celsius}. Once the coolant flow stopped
the temperature of the coaxial heater would immediate rise to the temperature of
the oven.

This was not a problem in the chosen biodiesel application, but better control
over the beginning of the temperature ramp would be necessary 

\section{Suggested design improvements}

\subsection{Four-wire resistance measurement}

The resistive heater had a design that depended on measuring the resistance of
the thin-walled stainless steel tube. The resistance was measured by comparing
the potential difference between the ends of the heater with the potential
difference over a reference resistor carrying an identical current. The circuit
that carried the current also measured the potential difference. Because the
current was high, the circuit had to be constructed in such a way that it no
other significant resistance in it, which meant that care had to be taken to
used heavy-guage cable and only use soldered joints. 

These troubles could have been avoided if the current circuit and the measuring
circuit were separated, using 'four wire' resistance measurement. In such a
design the potential difference is measure using a circuit that connects
directly to the voltmeter. The voltmeter has a high input impedance, which means
that the current that the circuit carries is low, and stray resistances will
play much less of a role. Also, this would have made it possible to use bolted
joints on the current-carrying circuit, which could have simplifed operations.

\subsection{Legs heating and cooling integrated in detector and inlet}


\subsection{Siltek-treated coaxial heater}


\todo{Discuss material that passes through column during trapping.}

\todos
